Analysis of split plot design using MCMCglmm

### 2017-08-24 02_MCMCglmm_analysis.Rmd
Clean up and detail the analysis document

For a quick overview, see this thread on Stack Overflow that walks through the output of `summary.MCMCglmm`,
which is used below. [R: Making sense of the output of a MCMCglmm](http://stackoverflow.com/questions/20993643/r-making-sense-of-the-output-of-a-mcmcglmm)

The MCMCglmm documentation is more in-depth but should still be referenced.
```{r MCMCglmm, eval=FALSE}
library(MCMCglmm)
vignette("Overview")
vignette("CourseNotes")
```

I found this CrossValidated topic to be useful in interpreting the outputs from
MCMCglmm as it explains the interpretation of the effects. While it is about
output from a `lmer`, the output is read in the same way, [How to interpret 2-way and 3-way interaction in lmer?](https://stats.stackexchange.com/questions/87412/how-to-interpret-2-way-and-3-way-interaction-in-lmer#87415).

@@

- 2015 `NRTE:0`

- 2015 `WMGT:FLD`

- 2016 `NRTE:60`

- 2016 `WMGT:FLD`

@@

#### MCMCglmm model fitting notes

@@

The `AUDPS` object is created when the project is loaded, in the file [munge/03_preprocess_data.R](./munge/03_preprocess_data.R). However, because it is a `tibble` and the treatments exist in a single column for graphing the raw data, this object needs a few minor changes to be usable for the analysis.

@@

Now that the `AUDPS_2015` and `AUDPS_2016` `data.frames` exist, we can start the analysis.

>>>>

The _MCMCglmm_ documentation provides an excellent resource for interpreting the outputs for each of the models below.

```{r MCMCglmm, eval=FALSE}
library(MCMCglmm)
vignette("Overview")
vignette("CourseNotes")
```

When comparing the treatments in the analysis, the model compares each treatment to the base (control) treatement.

@@

- 2015

    - `NRTE:0`

    - `WMGT:FLD`

- 2016

    - `NRTE:60`

    - `WMGT:FLD`

@@

#### _MCMCglmm_ model fitting notes

@@

The `AUDPS` object is created when the project is loaded, in the file [munge/03_preprocess_data.R](./munge/03_preprocess_data.R). However, because it is a `tibble()` and the treatments exist in a single column for graphing the raw data, this object needs a few minor changes to be usable for the analysis.

@@

Now that the `AUDPS_2015` and `AUDPS_2016` `data.frames()` exist, we can start the analysis.
